---
title: 'CPS Volunteerism Data Report'
author: ''
date: "`r Sys.Date()`"
output:
  html_document:
    css: customstyles.css
    self_contained: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = F,warning = F)
knitr::opts_chunk$set(out.width = "100%",fig.retina = 2)
library(tidyverse)
library(here)
library(plotly)
library(srvyr)
library(flextable)
library(officer)
library(here)
library(haven)
library(dplyr)
# 
# all_files <- list.files(here("dta/raw",""),".rds")
# all_files <- str_remove(all_files,".rds")
# all_files <- as.Date(all_files)
# all_files <- sort(all_files,decreasing = T)
# most_recentname <- all_files[1]
# most_recent <- all_files[1]
# most_recent <- paste(most_recent,".rds",sep ="")

```

# README

- This is the CPS Volunteer and Civic Life Supplement Survey Report (2017)




# Volunteer Status {.tabset}
Volunteer status in the past 12 months



## Overall

```{r}
data <- read_csv("data/dta1_vstatus17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Volunteer` = scales::percent(`Volunteer`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta1_vstatus17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Volunteer` = scales::percent(`Volunteer`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta1_vstatus17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Volunteer` = scales::percent(`Volunteer`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender
```{r}
data <- read_csv("data/dta1_vstatus17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Volunteer` = scales::percent(`Volunteer`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta1_vstatus17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Volunteer` = scales::percent(`Volunteer`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

#[VOLUNTEER ACTIVITY]

#Ver A: Civic & Political {.tabset}
Volunteer activity: civic, political, professional, international

## Overall

```{r}
data <- read_csv("data/dta_v_org_type1_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_type1_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_type1_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_v_org_type1_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_type1_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Ver B: Civic & Political {.tabset}
Volunteer activity: civic, political, professional, international

## Overall

```{r}
data <- read_csv("data/dta2_v_org_type1_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta2_v_org_type1_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta2_v_org_type1_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta2_v_org_type1_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta2_v_org_type1_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```



#Ver A: Education & Youth {.tabset}
Volunteer activity: Education & Youth Organizations

## Overall

```{r}
data <- read_csv("data/dta_v_org_type2_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_type2_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_type2_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender
```{r}
data <- read_csv("data/dta_v_org_type2_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_type2_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


#Ver B: Education & Youth {.tabset}
Volunteer activity: Education & Youth Organizations

## Overall

```{r}
data <- read_csv("data/dta2_v_org_type2_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta2_v_org_type2_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta2_v_org_type2_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender
```{r}
data <- read_csv("data/dta2_v_org_type2_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta2_v_org_type2_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```




#Ver A: Religious {.tabset}

## Overall
```{r}
data <- read_csv("data/dta_v_org_type6_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_type6_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_type6_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_v_org_type6_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_type6_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


#Ver B: Religious {.tabset}

## Overall
```{r}
data <- read_csv("data/dta2_v_org_type6_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta2_v_org_type6_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta2_v_org_type6_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta2_v_org_type6_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta2_v_org_type6_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```



#Ver A: Social & Community {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_v_org_type7_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_type7_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_type7_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_v_org_type7_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_type7_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Ver B: Social & Community {.tabset}

## Overall

```{r}
data <- read_csv("data/dta2_v_org_type7_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta2_v_org_type7_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta2_v_org_type7_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta2_v_org_type7_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta2_v_org_type7_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

#Ver A: Sports & Hobby {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_v_org_type8_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_type8_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_type8_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_v_org_type8_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_type8_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Ver B: Sports & Hobby {.tabset}

## Overall

```{r}
data <- read_csv("data/dta2_v_org_type8_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta2_v_org_type8_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta2_v_org_type8_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta2_v_org_type8_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta2_v_org_type8_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  mutate(`Not a volunteer` = scales::percent(`Not a volunteer`,accuracy = 1)) %>% 
  knitr::kable()
```


# Discussing Politics {.tabset}
Discussing politics with Family and Friends
## Overall

```{r}
data <- read_csv("data/dta_dis_poli_ff_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_dis_poli_ff_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_dis_poli_ff_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_dis_poli_ff_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_dis_poli_ff_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```



#Diversity Interaction {.tabset}
Frequency of talking to people of different racial/ethnic/cultural background

## Overall
```{r}
data <- read_csv("data/dta_dis_dif_rac_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_dis_dif_rac_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_dis_dif_rac_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_dis_dif_rac_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_dis_dif_rac_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```



#Political News {.tabset}
Follow political News or Local Issues
## Overall

```{r}
data <- read_csv("data/dta_follow_poli_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_follow_poli_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_follow_poli_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_follow_poli_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_follow_poli_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Basically every day` = scales::percent(`Basically every day`,accuracy = 1)) %>% 
  mutate(`A few times a week` = scales::percent(`A few times a week`,accuracy = 1)) %>%
  mutate(`A few times a month` = scales::percent(`A few times a month`,accuracy = 1)) %>% 
  mutate(`Once a month` = scales::percent(`Once a month`,accuracy = 1)) %>% 
  mutate(`Less than once a month` = scales::percent(`Less than once a month`,accuracy = 1)) %>% 
  mutate(`Not at all` = scales::percent(`Not at all`,accuracy = 1)) %>% 
  knitr::kable()
```



#Voted Local Election {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_voted_localE_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_voted_localE_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_voted_localE_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_voted_localE_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>%
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_voted_localE_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Attended Public Meeting {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_attend_meeting_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_attend_meeting_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_attend_meeting_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_attend_meeting_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_attend_meeting_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Contact Public Office {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_contact_office_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_contact_office_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_contact_office_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_contact_office_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_contact_office_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Boycotting {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_boycoott_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_boycoott_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_boycoott_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_boycoott_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_boycoott_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Belong to Any Orgs {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_org_belong_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_org_belong_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_org_belong_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_org_belong_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_org_belong_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```



#Volunteered in Any Orgs {.tabset}

## Overall

```{r}
data <- read_csv("data/dta_v_org_17.csv")
data %>% 
  filter(type == "Overall") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```


## Race
```{r}
data <- read_csv("data/dta_v_org_17.csv")
data %>% 
  filter(type == "Race") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


## Age Groups
```{r}
data <- read_csv("data/dta_v_org_17.csv")
data %>% 
  filter(type == "Age Group") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```

## Gender

```{r}
data <- read_csv("data/dta_v_org_17.csv")
data %>% 
  filter(type == "Gender") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()

```

## Educational Attainment

```{r}
data <- read_csv("data/dta_v_org_17.csv")
data %>% 
  filter(type == "Education") %>% 
  select(-type) %>% 
  rename(Region = region,
         Group = group) %>% 
  mutate(`Yes` = scales::percent(`Yes`,accuracy = 1)) %>% 
  mutate(`No` = scales::percent(`No`,accuracy = 1)) %>% 
  knitr::kable()
```


